Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Discuss blockage in conclusions; resolves #49
Fix up conclusions a bit

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity---a better predictor than conventional
quantifications of airfoil performance, e.g., lift-to-drag ratio. Note that this
method is not restricted to standard symmetrical NACA foils. The simple peak
geometric torque coefficient model predicted Reynolds number independence for
Reynolds numbers based on blade chord of $Re_c > 2 \times 10^5$. Is it also
shown from this metric that foils with higher camber are more Reynolds number
dependent at lower Reynolds number but have smaller slopes in the linear regime.
The Reynolds number dependence of the peak torque coefficient calculated from
static foil data and cross-flow turbine kinematics was shown to be a reasonable
indicator for predicting Reynolds number dependence of an actual cross-flow
turbine operating under dynamic conditions, including dynamic stall.

At lower Reynolds numbers we observed lower levels of turbulence in the wake at
$x/D=1$, along with lower levels of turbulent transport with respect to mean
streamwise momentum and mean kinetic energy recovery in the streamwise
direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection was enhanced at high $Re$. Despite being order of
magnitude smaller than other transport processes, viscous diffusion increased
rapidly with decreasing $Re$, and is expected to become significant to the wake
dynamics around $Re_D \sim 10^4$. Overall, the total wake transport measured
leveled off at essentially the same Reynolds number that the performance did.

From these results we can make the recommendation that physical model tests be
on the order $Re_D \sim 10^6$ to provide predictions of full-scale performance.
This threshold also applies to the validation of predictive engineering models,
especially for high-fidelity CFD models, where the boundary layer is to be
resolved, since transition to turbulence plays an important role in overall
blade loading.

>>>>

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity---a better predictor than conventional
quantifications of airfoil performance, e.g., lift-to-drag ratio. Note that this
method is not restricted to standard symmetrical NACA foils, though those
evaluated here with higher camber were more sensitive at lower $Re$ but had
smaller slopes in the linear regime.

At lower Reynolds numbers we observed lower levels of turbulence in the wake at
$x/D=1$, along with lower levels of turbulent transport with respect to mean
streamwise momentum and mean kinetic energy recovery in the streamwise
direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection was enhanced at high $Re$, which may be due to larger
free surface deformation reducing the near-wake's cross-sectional area. Despite
being order of magnitude smaller than other transport processes, viscous
diffusion increased rapidly with decreasing $Re$, and is expected to become
significant to the wake dynamics around $Re_D \sim 10^4$. Overall, the total
wake transport measured leveled off at essentially the same Reynolds number that
the performance did.

From these results we can make the recommendation that physical model tests be
on the order $Re_D \sim 10^6$ to provide predictions of full-scale performance.
This threshold also applies to the validation of predictive engineering models,
especially for high-fidelity CFD models, where the boundary layer is to be
resolved, since transition to turbulence plays an important role in overall
blade loading. Note that in our case blockage, though reasonably low, may be
increasing flow through the turbine compared with a free case, which could mean
$Re$ thresholds for free flows could be slightly higher, though a reliable
blockage correction algorithm has not yet been agreed upon for CFTs
\cite{Cavagnaro2014}.
